Stimjim: open source hardware for precise electrical stimulation

### 2019-05-12 benchmarking/paper/draft2.Rnw
fixed leading space in paramStringFile, updated analysis

plot(paramMat[61:90,5], sapply(res[seq(121,180,by=2)], function(x) x$sh.median*1e3), 
  log='', main='amplitude vs target', xlab='Target amplitude (mV)', ylab='measured amplitude (mV)', cex=0.75)
abline(a=0,b=1.0)
points(paramMat[61:90,5], sapply(res[seq(122,180,by=2)], function(x) x$sh.median*1e3),
  col='red', cex=0.75)

>>>>

x = c(paramMat[61:90,5], -paramMat[61:90,5])
y = t(sapply(res[seq(121,180,by=2)], function(x) c(x$sh.median,x$sl.median))*1e3)
plot(x,y, main='Voltage accuracy', xlab='Target amplitude (mV)', ylab='measured amplitude (mV)', cex=0.75)
abline(a=0,b=1.0)

x = c(paramMat[61:90,6], -paramMat[61:90,6])
y = t(sapply(res[seq(122,180,by=2)], function(x) c(x$sh.median,x$sl.median))/9750*1e6)
plot(x,y, main='Current accuracy', xlab='Target amplitude (uA)', ylab='measured amplitude (uA)', cex=0.75, col='red')
abline(a=0,b=1)
